### 2017-06-20 paper.tex
How to use feedback
Moving figure to end of paper
Adding reference for faculty not having pedagogy training

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education,
this knowledge and expertise is rarely transferred into classroom practice.

@@

\bibitem{lessons-learned}
Wilson G.
\newblock Software Carpentry: Lessons Learned.
\newblock F1000Research. 2016;3(62).
\newblock doi:{10.12688/f1000research.3-62.v2}.

\bibitem{instructor-training}
Christina Koch and Greg Wilson (eds.)
\newblock Software Carpentry: Instructor Training; 2016.
\newblock \url{https://zenodo.org/record/57571#.WS8huDOZPdQ}.

@@

\bibitem{shell2015}
Gabriel A.~Devenyi and Christina Koch (eds.):
Software Carpentry: The Unix Shell; 2015.
\newblock \url{https://zenodo.org/record/27355#.WS8lajOZPdQ}.

\bibitem{shell2017}
Gabriel A.~Devenyi and Ashwin Srinath (eds.):
Software Carpentry: The Unix Shell; 2017.
\newblock \url{https://zenodo.org/record/278226#.WS74tTOZPdQ}.

\bibitem{choral-explanations}
Caulfield M. Choral Explanations; 2016.
\newblock https://hapgood.us/2016/05/13/choral-explanations/.

@@

\bibitem{git-survey}
GitLab
\newblock Global Developer Survey.
\newblock http://get.gitlab.com/global-developer-survey/; 2016.

>>>>

Decades of pedagogical research has yielded many insights into
how best to build and deliver lessons \cite{hlw}.
Unfortunately,
since most college and university faculty have little or no training in education \cite{browning2012},
this knowledge and expertise is rarely transferred into classroom practice.

@@

\bibitem{lessons-learned}
Wilson G.
\newblock Software Carpentry: Lessons Learned.
\newblock F1000Research, 3(62), 2016,
\newblock 10.12688/f1000research.3-62.v2.

\bibitem{instructor-training}
Koch C. and Wilson G. (eds.)
\newblock Software Carpentry: Instructor Training; 2016.
\newblock \url{https://zenodo.org/record/57571#.WS8huDOZPdQ}.

@@

\bibitem{shell2015}
Devenyi G.~A. and Koch C. (eds.):
Software Carpentry: The Unix Shell; 2015.
\newblock \url{https://zenodo.org/record/27355#.WS8lajOZPdQ}.

\bibitem{shell2017}
Devenyi G.~A. and Srinath A. (eds.):
Software Carpentry: The Unix Shell; 2017.
\newblock \url{https://zenodo.org/record/278226#.WS74tTOZPdQ}.

\bibitem{choral-explanations}
Caulfield M. Choral Explanations; 2016.
\newblock \url{https://hapgood.us/2016/05/13/choral-explanations/}.

@@

\bibitem{git-survey}
GitLab
\newblock Global Developer Survey.
\newblock \url{http://get.gitlab.com/global-developer-survey/}, 2016.

\bibitem{browning2012}
Brownell S.~E. and Tanner K.~D.:
Barriers to faculty pedagogical change: Lack of training, time, incentives, and...tensions with professional identity?
\newblock CBE Life Sciences Education,
\newblock 11(4), 2012,
\newblock 10.1187/cbe.12-09-0163.
